Effective Reionization Likelihood from Planck 2018 Data (?)

### 2021-03-22 paper/rei.tex

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]
%normalized by area
%{results/tau_posterior_comparisons/pl18_tau_posterior_tanh_vs_tanh_highz_vs_pc_dz_auto_zre_prior_6p1_normalized_by_area.pdf}
%normalized by max
{paper/plots/pl18_tau_posterior_tanh_vs_tanh_highz_vs_pc_dz_auto_zre_prior_6p1_normalized_by_max.pdf}
\caption{Posterior for the total optical depth in the PC analysis (shaded) and for a tanh (black solid line) and two-step model (blue dashed line)}. 
\label{fig:plot_tau_posterior_PC_vs_tanh_vs_tanh_highz}
\label{fig:tauPC}
\end{figure}

>>>>

\begin{figure}[ht]
\includegraphics[width=0.48\textwidth]
%normalized by area
%{results/tau_posterior_comparisons/pl18_tau_posterior_tanh_vs_tanh_highz_vs_pc_dz_auto_zre_prior_6p1_normalized_by_area.pdf}
%normalized by max
{paper/plots/pl18_tau_posterior_tanh_vs_tanh_highz_vs_pc_dz_auto_zre_prior_6p1_normalized_by_max.pdf}
\caption{Posterior of the total optical depth for the PC analysis (shaded), the tanh model (black solid line) and the two-step model (blue dashed line)}. 
\label{fig:plot_tau_posterior_PC_vs_tanh_vs_tanh_highz}
\label{fig:tauPC}
\end{figure}
